\plaintitle

### 2018-04-03 paper/paper.tex
...

People don't use online help
\cite{Novick:2006:WDP:1166324.1166329}.

@@

Gitsome(https://github.com/donnemartin/gitsome)
helps \texttt{git} users by
showing possible arguments and manuals on the Unix shell,
just like {\GH}.
The goal of Git some is alomost the same as {\GH}, but
Gitsome does not support ...

@@

% 補完系IDEいろいろ
% Miller方面いろいろ

\subsection{Context-based help}

\subsection{Use cloud data for development}

@@

% 他人の情報利用する系
% コード共有、コンパイルエラー共有

@@

@@

Jupyter
Eve

% 文芸的プログラミング
% JavaDoc, Jupyter, Eve

@@

>>>>

People don't use online help
\cite{Novick:2006:WDP:1166324.1166329}.
Twitterでのアンケート: 80\% が全然使わない

@@

Gitsome(https://github.com/donnemartin/gitsome)
helps \texttt{git} users by dynamically
showing possible arguments and related manuals on the Unix shell,
just like {\GH}.
The goal of Git some is alomost the same as {\GH} and we agree with its concept,
but Gitsome does not support ...

@@

\subsection{Using cloud data for development}
% 他人の情報利用する系
% コード共有、コンパイルエラー共有

@@

@@

Literate Programming\cite{Knuth}

@@

JavaDoc
Jupyter
Eve

@@

\section{Conclusion}
